Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s} = 13$~TeV

### 2020-06-01 sec_results.tex
update on results

To further observe the behavior of the ridge yield in events including hard processes,

the two-dimensional associated yield per trigger particle is measured with the leading track selection as shown in Figure 4. The ridge is still visible in the events where $\it{p}_{\rm{T}}^{\rm{Lead}}>$7 GeV/c, which means that the ridge co-exists with hard-scattering in pp collisions.

@@

\begin{figure}
	\centering
	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrl1.pdf} }
	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrl2.pdf} }
	\caption{ Two-dimensional associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class. The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} for the plots. Threshold for leading track selection is 5 GeV/\it{c}\rm{} (left) and 7 GeV/\it{c}\rm{} (right), respectively. }
\end{figure}

>>>>

To further observe the behavior of the ridge yield in events including hard processes, the correlations function is measured with minimum $\it{p}_{\rm{T, Lead}}$ or $\it{p}_{\rm{T, Jet}}$ selection for 1.0$<\it{p}_{\rm{T, assoc}},\,\it{p}_{\rm{T, trig}}<$2.0 GeV/\it{c}\rm{}, where the ridge yield is maximum.

@@

\begin{figure}[h!]
	\centering
	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrlh.pdf} }
	\subfigure{ \includegraphics[width=0.4\textwidth]{./figures/corrjet.pdf} }
	\caption{ Two-dimensional associated yield per trigger particle as function of $\Delta\eta$ and $\Delta\varphi$ in top 0-0.1\% multiplicity class. The interval of transverse momentum of trigger particle and associated particle is 1.0$<\it{p}_{\rm{T}}<$2.0 GeV/\it{c}\rm{} for the plots. Threshold for leading track selection is 5 GeV/\it{c}\rm{} (left) and 7 GeV/\it{c}\rm{} (right), respectively. }
\end{figure}
